Observed vs. Simulated Year Comparison

### 2023-06-28 03-post-process/ms-content/ms-content.Rmd
Create the time elapsed table

  row_spec(0, bold = TRUE) %>%
  column_spec(1, monospace = TRUE) %>%
  row_spec(nrow(tab), bold = TRUE)
```

>>>>

```{r time-table}
# calculate times elapsed for each chunk
tab = data.frame(
  Item = names(start_times),
  Minutes = round(sapply(1:length(start_times), function(i) lubridate::int_length(lubridate::int_diff(c(start_times[[i]], end_times[[i]])))/60), 1)
)

# add a total time elapsed
tab = rbind(tab, data.frame(Item = "Total", "Minutes" = sum(tab$Minutes)))

# create the table
kbl(tab, format = "latex", booktabs = TRUE, longtable = FALSE, linesep = "", caption = "Time elapsed in calculating the content in this document.") %>%
  kable_styling(full_width = FALSE, latex_options = "HOLD_position") %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1, monospace = TRUE) %>%
  row_spec(nrow(tab), bold = TRUE)
```
